AttCRISPR : an spacetime interpretable model for sgRNA efficiency prediction

### 2020-09-11 Paper/main.tex
9-11 fix RNN

@@

@@

\subsubsection{Attention module and model in spatial domain}

\subsubsection{Attention module and model in temporal domain}

>>>>

\subsection{Sequence encoding}

@@

\subsubsection{Spatial attention module}

\subsubsection{Temporal attention module}

@@

\begin{figure}[!tpb]%figure2
    \centerline{\includegraphics[scale=0.5]{category.png}}
    \caption{The overview of AttCRISPR. 
    It consists of two components, namely CNNs and RNNs. 
    The CNN component is used to capture spatial nucleotide preference, 
    while the RNN component is used to capture temporal nucleotide preference. 
    Finally, a weighted average method with trainable weight is used to predict activity.}\label{fig:02}
\end{figure}
